Supplementary Materials

### 2020-05-07 analysis/analysis.Rmd
Added correlation back in

filter(df, p == 0.95)

>>>>

filter(df, p == 0.95)
```

# Additional Analysis

## Index and Normality

## Correlation Between EEG RMS and Display Duration Threshold

Finally, we will investigate whether there is a correlation between the EEG rms measures and our display duration thresholds. As our two different measures come from different samples of participants, we are unable to do a direct comparison. However, we can use the results of the models discussed in Section 3 and compare p(eeg difference >0 | data) correlates with p(display duration difference < 0 | data).

```{r compare_comparisons}

bind_rows(
  select(comp_summary$eeg, measurement, key, mean_value),
  select(comp_summary$threshold, measurement, key, mean_value)) %>%
  spread(measurement, mean_value) -> d

m <- brm(data = d, threshold ~ rms)

bayes_R2(m)
```

We can see that although the correlation is relatively weak, our confidence interval indicates that we can be reasonably positive that $R^2>0$ (i.e, $95\%$ credible interval is 0.026 - 0.302$).

```{r fig.cap="Scatter plot showing the correlation between our two measures. Each line is a sample from the posterior of a Bayesian linear regression."}
d %>% 
  modelr::data_grid(rms = seq(-0.2, 0.8, 0.1)) %>%
  add_fitted_draws(m, n = 100) %>%
  ggplot(aes(x = rms, y = threshold, color = index)) +
  geom_line(aes(y = .value, group = .draw), alpha = .1, colour = "thistle4") +
  geom_point(data = d) +
  theme_minimal() + 
  ggthemes::scale_colour_ptol()
